%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape James Cheng} \\ \vspace{1pt}
    \small \href{mailto:jzcheng@stanford.edu}{\underline{jzcheng@stanford.edu}} $|$
    \href{https://www.linkedin.com/in/jamescheng24/}{\underline{linkedin.com/in/jamescheng24/}} $|$
    \href{https://github.com/jameszcheng}{\underline{github.com/jameszcheng}} $|$
    \href{https://jameszcheng.github.io/}{\underline{jameszcheng.github.io}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stanford University}{Stanford, CA}
      {M.S. in Computer Science, Artificial Intelligence Specialization}{Expected Jun. 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Courses}: Training Data for AI, Reinforcement Learning, NLP, Computer Vision, Robot Autonomy \& Perception}
      \resumeItemListEnd
    \resumeSubheading
      {University of California, Berkeley - Regents' and Chancellor's Scholar}{Berkeley, CA}
      {B.A. in Computer Science and B.S. in Business Administration, GPA: 3.92/4.00}{Aug. 2020 -- May 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Courses}: Algorithms, Operating Systems, Machine Learning, Data Structures, Random Processes, Optimization}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Stanford CS}{Stanford, CA}
        {Research Engineer - The Movement Lab}{Sep. 2025 -- Present}
        \resumeItemListStart
            \resumeItem{Reimplementing motion imitation methods (DeepMimic, AMP, ASE, ADD) in MuJoCo Lab with the Isaac Lab API, enabling scalable humanoid motion control and policy learning on GPU-parallel simulators}
        \resumeItemListEnd

        \resumeSubSubheading
        {Teaching Assistant (CS234: Reinforcement Learning, CS161: Design \& Analysis of Algorithms)}{Sep. 2025 -- Present}
        \resumeItemListStart
            \resumeItem{Guiding 100+ graduate students through implementations of PPO, RLHF, and DPO in PyTorch/MuJoCo (CS 234); leading office hours on dynamic programming, graph theory, and randomized algorithms for 300+ students (CS 161)}
        \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Sunnyvale, CA}
      {Software Engineering Intern - Kindle}{Jun. 2025 -- Sep. 2025}
      \resumeItemListStart
        \resumeItem{Architected backend integration for on-device AI image generation, orchestrating low-latency communication between constrained Kindle hardware (C++) and cloud inference (AWS Bedrock/Lambda)}
      \resumeItemListEnd

    \resumeSubheading
      {UC Berkeley EECS}{Berkeley, CA}
      {Undergraduate Research Assistant - BAIR Lab (Advised by Prof. Shankar Sastry)}{Jun. 2023 -- May 2024}
      \resumeItemListStart
        \resumeItem{Developed a follower-agnostic convergent algorithm for traffic routing Stackelberg Games; ran numerical experiments across 12 trajectories, tuning step-size, perturbation, and regularization parameters to verify convergence to stationary points; \textbf{paper accepted to CDC 2024}}
      \resumeItemListEnd

      \resumeSubSubheading
        {Teaching Assistant (CS 70: Discrete Mathematics and Probability)}{Aug. 2022 -- May 2024}
      \resumeItemListStart
        \resumeItem{Led weekly discussions, held office hours, and graded assignments for 500+ students across 4 semesters, covering proofs, graph theory, modular arithmetic, computability, and probability}
      \resumeItemListEnd

    \resumeSubheading
      {RUCKUS Networks - CommScope}{Sunnyvale, CA}
      {Software Engineering Intern}{Jun. 2023 -- Aug. 2023}
      \resumeItemListStart
          \resumeItem{Built Airbyte data connectors in Python to ingest 10k+ daily records into BigQuery; created Docker containers and Bitbucket CI/CD pipelines to automate testing and deployment}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Constrained Text Generation Benchmark (CTG)} $|$ \emph{Python, Together API, Anthropic API, spaCy}}{\textit{Jan. 2026 -- Present}}
        \resumeItemListStart
          \resumeItem{Designed a \textbf{348-prompt} benchmark (local / global / hybrid constraints) with dual-path verification (programmatic + LLM) to quantify autoregressive constraint-following limitations across 6 LLMs on \textbf{7,889 expanded variants}}
          \resumeItem{Built SFT and DPO fine-tuning pipelines on Together AI and meta-ablation analyses, confirming a steep difficulty gradient (local 37--53\% vs.\ global 12--21\% pass rates) driven by planning bottlenecks}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{LLM-as-Planner vs RL on Procgen} $|$ \emph{PyTorch, StableBaselines3, Amazon Bedrock}}{\textit{Mar. 2025 -- Jun. 2025}}
          \resumeItemListStart
            \resumeItem{Built hybrid RL-LLM agents with entropy-based mode switching, boosting task success rates up to 2$\times$ over RL-only baselines (PPO, DQN) across procedurally generated environments}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, CUDA, Rust, Java, SQL} \quad
     \textbf{ML/Tools}{: PyTorch, MuJoCo, NumPy, AWS, Docker, Git, GCP}
    }}
 \end{itemize}

\end{document}
